Effect of quality-adjusted production function inputs

### 2015-06-01 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Now using the model to extract fitted_and_resid_data. This streamlines the code quite a bit.

<<Fitted_and_Residuals>>=
temp_data <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), f = function(mod, id){
  df <- select(mod$data, Year, iGDP, Country)
  # Trim fitted to be same length as df to eliminate problems with possible NAs at end of fitted
  df$fitted <- yhat(mod)[c(1:length(df$Year))]
  df$Residuals <- resid(mod)[c(1:length(df$Year))]
  # Parse the id to find out whether this is quality-adjusted data
  id_list <- strsplit(id, split = "[.]")[[1]]
  df$flavor <- if (id_list[[2]] == "unadjusted") "Unadjusted" else "Quality-adjusted"
  df$energy <- if (id_list[[3]] == "noE") "Without energy" else "With energy"
  df$model <- id_list[[4]]
  df$nest <- if (length(id_list) > 4) id_list[[5]] else NA
  return(df)  
}) %>% do.call(rbind, .)

@@

We can also calculate the average values for $\Delta \lambda$ and $\Delta r$ 
as shown in Table~\ref{tab:traj.means.CD}.
%
<<Trajectory_Means_CD, results="asis">>=
xtable::xtable(filter(traj.data.means, model=="CD") %>% select(-nest),
               caption="Average $\\Delta\\lambda$ and $\\lambda r$ for Cobb-Douglas models.",
               label="tab:traj.means.CD", 
               digits=6) %>% 
  print(., 
        caption.placement="top", 
        size="\\tiny", 
        include.rownames=FALSE, 
        math.style.negative=TRUE)
@
%
These results for the Cobb-Douglas model indicate that 
we should perform the same analysis for the CES model.

>>>>

<<Fitted_and_Residuals>>=
fittedAndResidData <- function(model){
  df <- data.frame(select(model$data, Year))
  # Trim fitted to be same length as df to eliminate problems with possible NAs at end of fitted
  df$fitted <- yhat(model)[c(1:length(df$Year))]
  df$Residuals <- resid(model)[c(1:length(df$Year))]
  return(df)  
}

temp_data <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, id){
  df <- fittedAndResidData(model)
  f <- model$formula
  response <- summands(f, right = FALSE)
  df[[response]] <- model$data[[response]] # Add iGDP to the data frame
  id_list <- strsplit(id, split = "[.]")[[1]]
  df$Country <- id_list[[1]]
  df$flavor <- if (id_list[[2]] == "unadjusted") "Unadjusted" else "Quality-adjusted"
  df$energy <- if (id_list[[3]] == "noE") "Without energy" else "With energy"
  df$model <- id_list[[4]]
  df$nest <- if (length(id_list) > 4) id_list[[5]] else NA
  return(df)  
}) %>% do.call(rbind, .)

@@

We can also calculate the average values for $\Delta \lambda$ and $\Delta r$ 
as shown in Table~\ref{tab:traj.means.CD}.
%
<<TrajMeansTableFunction>>=
trajMeansTable <- function(data, caption, label){
  table <- xtable::xtable(data, caption=caption, label=label, digits=6)
  print(table, 
        caption.placement="top", 
        size="\\tiny", 
        include.rownames=FALSE, 
        math.style.negative=TRUE)
}
@

<<Trajectory_Means_CD, results="asis">>=
trajMeansTable(data = filter(traj.data.means, model=="CD") %>% select(-nest), 
               caption = "Average $\\Delta\\lambda$ and $\\Delta r$ for Cobb-Douglas models.",
               label="tab:traj.means.CD")
# xtable::xtable(filter(traj.data.means, model=="CD") %>% select(-nest),
#                caption="Average $\\Delta\\lambda$ and $\\Delta r$ for Cobb-Douglas models.",
#                label="tab:traj.means.CD", 
#                digits=6) %>% 
#   print(., 
#         caption.placement="top", 
#         size="\\tiny", 
#         include.rownames=FALSE, 
#         math.style.negative=TRUE)
@
%
These results for the Cobb-Douglas model indicate that 
we should perform the same analysis for the CES model.
